SST_patterns

### 2019-09-27 SST_patterns.Rmd
Corrected between different longitude schemes
Getting rid of NA
Update

```{r, fig.cap = "Windrose diagram representing the wind direction and speed for each of the sites", fig.height = 10, fig.width = 20}
library(ggradar)
library(dplyr)
library(scales)
library(tibble)
load("Data/UI_angle.RData")

@@

wind_daily_renamed <- UI_angle %>% 
  dplyr::rename(spd = mean_speed) %>%
  dplyr::rename(dir = dir_circ)

@@

p.wr3 <- p.wr2 + facet_wrap(.~ site, ncol = 4, nrow = 5) +
  theme(strip.text.x = element_text(size = 25))
p.wr3

@@

load("Data/UI_angle.RData")

wind_plot_prep <- UI_angle %>% 
  select(-t, -ui.saws)

wind_plot <- wind_plot_prep %>% 
  as_tibble(rownames = "site") %>% 
  group_by(site) %>% 
  mutate_at(vars(-site), rescale) %>% 
  tail(4)

ggradar(wind_plot)

??countmax

>>>>

```{r, fig.cap = "Windrose diagram representing the wind direction and speed for each of the sites", fig.height = 10, fig.width = 15}
library(ggradar)
library(dplyr)
library(scales)
library(tibble)
load("Data/UI_angle.RData")

@@

wind_daily_renamed <- UI_angle %>% 
  mutate(dir_circ = ifelse(dir_circ < 0, dir_circ+360, dir_circ)) %>% 
  dplyr::rename(spd = mean_speed) %>%
  dplyr::rename(dir = dir_circ) %>% 
  filter(spd > 0)

@@

p.wr3 <- p.wr2 + facet_wrap(.~ site, ncol = 2, nrow = 2) +
  theme(strip.text.x = element_text(size = 25))
p.wr3

@@

# load("Data/UI_angle.RData")
# 
# wind_plot_prep <- UI_angle %>% 
#   select(-t, -ui.saws)
# 
# wind_plot <- wind_plot_prep %>% 
#   as_tibble(rownames = "site") %>% 
#   group_by(site) %>% 
#   mutate_at(vars(-site), rescale) %>% 
#   tail(4) 
# 
# ggradar(wind_plot)
# 
# ??countmax
